---
title: "TITLE"
author: "Adrian Wong, Yingying Zhou, Xinyi Xu, Yang Wu "
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
 bookdown::pdf_document2:
 toc: no
subtitle: "SUBTITLE"
abstract: "ABSTRACT"
thanks: 'Code and data are available at: https://github.com/yangg1224/groupproject-.git'
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
#install.packages("PerformanceAnalytics")
library("PerformanceAnalytics")

```

# Introduction
```{r}

```

# Data 

## Intervention 

## Data Gathering Method 

## Descriptive Analysis

```{r read_data, include=FALSE}

setwd("~/Downloads/Git/groupproject-") 

# read raw dataset from scripts, need to run survey_response _simulation first.
simulated_data<- read_csv("inputs/simulated_data.csv") 

# We add a new column To distinguish the restaurant size by employees number. 
# if employees number >20 then we define it is big, otherwise it is small.
for (i in 1:nrow(simulated_data)){
  if ((simulated_data$Q8[i] == ">30") || (simulated_data$Q8[i] == "20-30")){
  simulated_data$size[i] = "Big"  
  }else {
    simulated_data$size[i] = "Small"
  }
}

treated_data<-
  filter(simulated_data, simulated_data$type == "Treated" ) # load treated data 

control_data<-
  filter(simulated_data, simulated_data$type == "Control" ) # load control data
```

### Revenue distributions group by restaurant size
```{r revenue_distribution, echo=FALSE}


library(ggplot2)
# Treated group
rd1<-
  ggplot(treated_data, aes(x = treated_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 40, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Treated Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_linedraw()
# Control group
rd2<-
  ggplot(control_data, aes(x = control_data$Q13)) +
  geom_histogram(aes(color = size, fill= size),
                position = "identity", bins = 40, alpha=0.5) +
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"))+
  labs(title="Revenue Distributions in Control Group", x="Renvenue", y="Count")+
  geom_density(alpha=.2, fill="#FF6666")+
  theme_linedraw()
# combine two diagram in one graph
#install.packages("ggpubr")
library(ggpubr)
ggarrange(
  rd1, rd2, 
  ncol = 1, nrow = 2,
  heights = c(1, 1),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

```

### restaurant type by regions

```{r restaurant_type, echo=FALSE}

library(viridis)


# Treated group
rt1<-
  ggplot(treated_data, aes(fill= Q3, x= Q2)) +
  geom_bar(position="stack", stat="count")+
    ggtitle("Treated Group: Restaurant Types in different regions") +
    xlab("Regions")+
    ylab("Count of Numbers")+
    theme_grey()

    
rt1<- rt1 + guides(fill=guide_legend(title="Types")) # change the Legend title 

# Control group
rt2<-
  ggplot(control_data, aes(fill= Q3, x= Q2)) +
  geom_bar(position="stack", stat="count")+
    ggtitle("Control Group: Restaurant Types in different regions") +
    xlab("Regions")+
    ylab("Count of Numbers")+
    theme_grey()
    
rt2<- rt2 + guides(fill=guide_legend(title="Types")) # change the Legend title 
# combine two diagram in one graph
ggarrange(
  rt1, rt2, 
  ncol = 2, nrow = 1,
  vjust = 1,
  widths = c(2, 2),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

```


### Flex and fiexed cost changes 

```{r felx_fix, echo=FALSE, fig.width=10, fig.height=4}



# Treated group

# Fixed costs 
fixc1<-
  ggplot(treated_data, aes(fill= Q11, x=Q11)) +
  geom_bar(stat="count", width = 0.5)+
    ggtitle("Fixed costs changes") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()

fixc1<- fixc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title 

# flex cost
flexc1<-
    ggplot(treated_data, aes(fill= Q12, x=Q12)) +
    geom_bar(stat="count", width = 0.5)+
    ggtitle("Treated Group: Flexible costs changes") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()


flexc1<- flexc1 + guides(fill=guide_legend(title="Changes")) # change the Legend title 

# Control group
fixc2<-
  ggplot(control_data, aes(fill= Q11, x=Q11)) +
  geom_bar(stat="count", width = 0.5)+
    ggtitle("Fixed costs changes") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()

fixc2<- fixc2 + guides(fill=guide_legend(title="Changes")) # change the Legend title 

# flex cost
flexc2<-
    ggplot(control_data, aes(fill= Q12, x=Q12)) +
    geom_bar(stat="count", width = 0.5)+
    ggtitle("Control Group: Flexible costs changes") +
    coord_flip()+
    xlab("Changes")+
    ylab("Number of restaurants")+
    theme_minimal()


flexc2<- flexc2 + guides(fill=guide_legend(title="Changes")) # change the Legend title 



# combine two diagram in one graph
ggarrange(
  flexc1,fixc1,flexc2, fixc2,
  ncol = 2, nrow = 2,
  vjust = 1,
  widths = c(2, 2),
  align = "hv",
  common.legend = TRUE, legend = "bottom"
  )

```

### Distribution average employee salary
```{r salary_distribution, echo=FALSE, fig.width=10, fig.height=4}
library(ggthemes)
# Treated group
s1<-
  ggplot(treated_data, aes(x = Q2, y= Q9)) +
  geom_boxplot(outlier.colour="red", 
               outlier.shape=5,
               outlier.size=4) +
  labs(title="Salary Distributions in Treated Group", x="Regions", y="Hourly rate")+
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01)+ # add dots
  theme_economist()

# Control group
s2<-
  ggplot(control_data, aes(x = Q2, y= Q9)) +
  geom_boxplot(outlier.colour="red", 
               outlier.shape=5,
               outlier.size=4) +
  labs(title="Salary Distributions in Control Group", x="Regions", y="Hourly rate")+
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.01)+ #add dots
  theme_economist()


# combine two diagram in one graph

library(ggpubr)
ggarrange(
  s1, s2, 
  ncol = 2, nrow = 1,
  hjust = -0.5,
  align = "hv"
  )

```

### correlation matrix
```{r correlation, echo=FALSE, fig.width=10, fig.height=4}

```

# Discussion

## Overview 

## Findings 

### Finding ONE

### Finding TWO

### Finding THREE

## Limitation

## Future Directions 

```{r}

```

\newpage

# References
